Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change

### 2020-12-21 Manuscript/HI_Model_ms.Rmd
updated manuscript file

## Introduction
Terrestrial ecosystems are a major sink for atmospheric carbon dioxide (CO~2~), removing ~30% of human emissions on an annual basis [@friedlingstein_global_2019]. However, the strength of the land carbon sink remains highly uncertain because of its sensitivity to interannual variability in climate, land use, and land cover change [@ahlstrom_dominant_2015; @prestele_current_2017]. Accounting for climate and land-use variability has proven so difficult that annual estimates of terrestrial ecosystem carbon sequestration are often estimated indirectly by subtracting annual atmospheric and ocean carbon sink estimates from annual human CO~2~ emissions [@le_quere_global_2013; @friedlingstein_global_2019].

>>>>

## Introduction
Terrestrial ecosystems are a major sink for atmospheric carbon dioxide (CO~2~), removing ~30% of human emissions on an annual basis and reducing the rate of increase in atmospheric CO~2~ [@friedlingstein_global_2019]. However, the strength of the land carbon sink remains highly uncertain because of its sensitivity to interannual variability in climate, land use and land cover change [@ahlstrom_dominant_2015; @prestele_current_2017]. The uncertainty surrounding estimates of terrestrial carbon sequestration complicates efforts to employ "natural carbon solutions", defined as conservation, restoration, and land management interventions aimed at enhancing carbon storage in natural biological reservoirs [@griscom_natural_2017]. A growing number of sub-national jurisdictions have pledged to incorporate natural climate solutions as part of their stated goal to achieve carbon neutrality by mid-century [].
